% arara: pdflatex: { options:  [ '-halt-on-error' ] }
% arara: biber if exists(toFile('mypubs.bib')) && exists('bcf')
% arara: pdflatex: { synctex: yes } if exists('toc') || exists('bbl')
% arara: pdflatex: { synctex: yes } while (found('log', '(?<!rerunfilecheck.{15,20})Rerun'))
% arara: clean: { extensions: [ log, out, toc, bbl, bcf, blg, run.xml ] }

\documentclass{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[
	url=false,
	doi=false,
	date=year,
	isbn=false,
	sorting=ydnt,
	maxnames=10,
	defernumbers=true,
	style=nature
]{biblatex}

\addbibresource{mypubs.bib}

%% Commands to format the highlighting of my name in bibliographies

\renewcommand*{\mkbibnamegiven}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

%% Define format for sections of the CV

\newcommand{\cvtitle}[1]{%
	{\Large \textbf{#1}} \hfill {\large \textsc{Curriculum Vitae}}
	\hrule
}

\newcommand{\cvsection}[1]{%
	{\large \textbf{#1\phantom{,}}}
	\hrule
}

\setlength{\parindent}{0pt}

\nocite{*}

\begin{document}

%% Heading
\cvtitle{Philip Woods}
\bigskip
1200 E. California Blvd.	\hfill	Cell: (630) 723-7573\\
Mail Code 100-23			\hfill	pwoods@caltech.edu\\
Pasadena, CA 91125			\hfill	% website
\bigskip

%% Academic Positions
% Postdocs, professorships, etc.

%% Education
\cvsection{Education}
\bigskip

\textsc{California Institute of Technology, Pasadena, CA}\\
Ph.D. student, Geobiology		\hfill	2018 -- present\\
% Thesis:
Advisor: Victoria Orphan\\
Committee: Victoria Orphan, Jared Leadbetter, Dianne Newman, Woody Fischer, Joe Parker

\medskip

\textsc{Harvey Mudd College, Claremont, CA}\\
B.S., Joint Major in Chemistry and Biology	\hfill	May 2017\\
Graduated with Distinction\\
Thesis: \emph{The effects of ribosomal DNA copy number on lifespan, health, and dietary restriction.}\\
Advisor: Jae Hur

\bigskip

%% Research Interests
%\cvsection{Research Interests}
%\medskip
%
%asdf
%
%\bigskip

%% Fellowships, Honors, and Awards
\cvsection{Fellowships, Honors, and Awards}
\bigskip

Benjamin M. Rosen Graduate Fellowship, \emph{California Institute of Technology}	\hfill	2018\\
CEMI 1st Year Fellowship, \emph{California Institute of Technology}				\hfill	2018\\
Mindlin Prize for Innovative Ideas in the Sciences, \emph{Harvey Mudd College}		\hfill	2017\\
Best Senior Thesis in Biology, \emph{Harvey Mudd College}						\hfill	2017\\
Departmental Honors in Biology, \emph{Harvey Mudd College}					\hfill	2017%\\
%Dean's List, \emph{Harvey Mudd College}										\hfill	2012 -- 2013\\
%Superior Academic Performance, \emph{Harvey Mudd College}					\hfill	2011

\bigskip

%% Research Experience
\cvsection{Research Experience}
\bigskip

\textsc{California Institute of Technology}\\
Advisor: Victoria Orphan	\hfill	2019 -- present
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Built a comprehensive phylogeny of high-quality \emph{Methanomicrobiales} genomes.
\item
Used comparative genomics to identify distinctive genome features of the ANME-3 clade.
\item
Identified several key evolutionary processes in the evolution of ANME from methanogens.
\end{itemize}

\medskip

\textsc{California Institute of Technology}\\
Advisor: Jared Leadbetter	\hfill	2019 -- 2021
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Investigated the manganese-dependent growth potential of a novel \emph{Methylobacterium} isolate.
\item
Established growth yields and growth kinetics for the \emph{Methylobacterium} under several conditions.
\item
Assayed manganese oxidation in microbial cultures using spectrophotometry.
\end{itemize}

\medskip

\textsc{Northwestern University Center for Connected Learning and Computer-Based Modeling}\\
Advisors: Uri Wilensky and Hillary Swanson	\hfill	2017 -- 2018
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Developed multiple NetLogo computational models of CRISPR-Cas in bacterial cells and communities.
\item
Developed a NetLogo computational model of the evolution of anisogamy.
\item
Designed experiments using this model to address questions in theoretical biology literature.
\item
Developed and implemented high school science curricula to teach computational thinking.
\item
Designed assessments to evaluate the efficacy of these curricula.
\end{itemize}

\medskip

\textsc{Harvey Mudd College Biology Department}\\
Advisor: Jae Hur	\hfill	2016 -- 2017
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Designed and executed a research agenda independently as a senior thesis project.
\item
Investigated the molecular mechanisms behind dietary restriction-based lifespan extension.
\item
Performed lifespan, dietary restriction, stress, and qPCR assays on Drosophila.
\end{itemize}

\medskip

\textsc{Pomona College Biology Department}\\
Advisor: Melissa Petreaca	\hfill	2014
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Studied the role of the LIGHT protein in mouse neutrophil degranulation and NETosis.
\item
Analyzed NET formation using ELISA and fluorescence microscopy.
\end{itemize}

%\medskip
\pagebreak

\textsc{Harvey Mudd College Chemistry Department}\\
Advisor: Katherine	van Heuvelen		\hfill	2013
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Synthesized cyclam derived ligands for nickel complexes to model cofactor F430.
\item
Characterized these with Gaussian DFT calculations and UV-vis, NMR, and IR spectroscopy.
\item
Tested the model complexes for methane oxidation potential using spectrophotometry.
\end{itemize}

\bigskip

%% Teaching and Mentoring Experience
\cvsection{Teaching Experience}
\bigskip

{\large \textsc{California Institute of Technology}}
\medskip

\textsc{Certificate of Practice in University Teaching} \hfill 2019 -- present
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Received formal instruction in pedagogy and teaching practices.
\item
Apply these practices in a series of teaching experiences.
\item
Refine teaching practice based on feedback from students and teaching specialists.
\end{itemize}

\medskip

\textsc{Bi/Ge/ESE 105: Evolution} \hfill Winter 2020\\
Instructors: Victoria Orphan and Rob Phillips
\begin{itemize}[leftmargin=1.5em, nosep, label=$\vcenter{\hbox{\tiny\textbullet}}$]
\item
Developed and implemented classroom activities covering phylogeny, population genetics,
speciation, and coevolution.
\item
Helped facilitate weekly laboratory exercises on concepts and techniques relevant to evolution.
\end{itemize}

\bigskip

%% Supervised Students

%% Service & Outreach
% Conference organization, grant reviewing, journal referee, committees, etc.
\cvsection{Service \& Outreach}
\bigskip

{\large \textsc{California Institute of Technology}}
\medskip

Co-founder \& treasurer of the local chapter of the American Society for Microbiology \hfill 2022 -- present

\bigskip

%% Journal Publications
\cvsection{Peer Reviewed Publications}

\printbibliography[type=article,heading=none,resetnumbers=true]

%% Conference Submissions
\cvsection{Conference Submissions}

\printbibliography[type=inproceedings,heading=none,resetnumbers=true]

%% Professional Associations
\cvsection{Professional Associations}
\bigskip

American Society for Microbiology, Member \hfill 2022 -- present\\
Phi Lambda Upsilon, Member	\hfill	2017 -- present

\bigskip

%% Other Skills
\cvsection{Other Skills}
\bigskip

Proficient in building agent-based models.\\
Proficient with Python, NetLogo, Bash scripting, Anvi'o, and Matlab.\\
Experience with Javascript, C++,  Java, Igor Pro, and Racket.\\
Working proficiency in Portuguese.

\end{document}